---
title: "Hello R"
author: "Zach Morales"
date: "7/20/2021"
output: rmarkdown::github_document
---

```{r init, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Installing required packages

The below block of code installs the packages that will be used throughout the book.

```{r install, eval=FALSE}
install.packages(c("tidyverse", "nycflights13", "gapminder", "Lahman"))
```

### Loading packages

If packages have been installed, you can load them with the following.

```{r load}
library(tidyverse)
library(nycflights13)
library(gapminder)
library(Lahman)
```

### Running R code

Example of simple arithmetic.

```{r arithmetic}
1 + 2
```

### Constructing a reprex

A good minimal reproducible example makes it easier for other people to help you, and often you'll figure out the problem yourself in the course of making it.

1. Load packages at the top of the script (and ensure they are all updated to the latest version).
2. Use `dput()` to generate the R code needed to recreate a dataset and try to find the smallest subset of your data that still reveals the problem.
    + Run `dput(dataset)`.
    + Copy the output.
    + In the reprex type `dataset <- ` then paste the copied code.
3. Ensure that your code is easy for others to read (use spaces, ensure variables names are concise/informative, use comments to indicate where the problems lies, remove everything not related to the problem). Shorter code is easier to understand and easier to fix.
4. Ensure you actually have a reprex by starting a fresh R session and copying/pasting the script in.